PANCHANGE_data_preprocessing

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
add respiratory part with routing question

@@

```{r}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    comorbidity_total_count_factor_numeric =
      case_when(
    comorbidity_total_count_numeric == "0" ~ 0,
    comorbidity_total_count_numeric == "1" ~ 1,
    comorbidity_total_count_numeric == "2" ~ 2,
    comorbidity_total_count_numeric > 2 ~ 3
    )
  )

@@

>>>>

# NBR cohort information
```{r nbr cohort information}
if(NBR = TRUE){
  nbr.cohort <- readxl::read_xlsx(
    path = paste0(data.raw_path, "/nbr/coping_participants_export_20200730.xlsx")
    )

  dim(nbr.cohort)
  colnames(nbr.cohort)
  }

@@

```{r comordbitiy_total_count_factor}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    comorbidity_total_count_factor_numeric =
      case_when(
    comorbidity_total_count_numeric == "0" ~ 0,
    comorbidity_total_count_numeric == "1" ~ 1,
    comorbidity_total_count_numeric == "2" ~ 2,
    comorbidity_total_count_numeric > 2 ~ 3
    )
  )

@@

Probable COVID case including the routing question
```{r}
dat.glad.coping <- dat.glad.coping %>%
  mutate(
    covid_probable_case_incl_screening_numeric =
      case_when(
        respiratory.breath_diarrhoea_fatigue_fever_numeric == 0 ~ 0,
        covid_odds_ratio_50_numeric == 0 ~ 0,
        covid_odds_ratio_50_numeric == 1 ~ 1
      )
  )

#create factor with labels
dat.glad.coping <- dat.glad.coping %>%
  mutate(
    covid_probable_case_incl_screening =
      recode_factor(
        covid_probable_case_incl_screening_numeric,
        "0" = "No COVID",
        "1" = "Probable COVID"
      )
  )

dat.glad.coping %>%
  freq(covid_probable_case_incl_screening, 
     cumul = FALSE) 
```
